---
title: "Leveraging Machine Learning in R for Predicting Outcomes: A Case Study"
author: "Jagadish Katam"
format: pdf
editor: visual
execute: 
  echo: false
---

## Introduction

Artificial Intelligence (AI), Machine Learning (ML), Deep Learning (DL), and Data Science (DS) have been frequently interchangeably used. ML is a subset of AI that focuses on developing algorithms and models that enable computers to learn from and make predictions or decisions based on data, without being explicitly programmed.

## Data

```{r}
#| echo: false
#| output: false
#| eval: true
#| include: false

library(tidyverse)
# devtools::load_all()
source('R/logisticmodel.R')
logit <- logisticmodel('data/Liver_disease_data.csv')
```

```{r}
#| echo: false
head(logit$table)
```

{{< pagebreak >}}

## Box Plot

```{r}
logit$boxplot_figure
```

## Bar Chart

```{r}
logit$barplot_figure
```

{{< pagebreak >}}

## Model Summary

```{r}
logit$model_summary
```

{{< pagebreak >}}

## Model Accuracy

```{r}
logit$accuracy
```

## Confusion Matrix

```{r}
logit$confusion_matrix
```

{{< pagebreak >}}

## Receiver Operating Characteristic (ROC) 

```{r}
logit$roc_curve
```

```{r}
logit$roc_curve |> plot()
```

{{< pagebreak >}}

## Predicted Probabilities

```{r}
logit$predicted_probabilities
```
